\section{KahaDB: A primer}
\label{sec:kahadb}
	\subsection{What is KahaDB?}
	KahaDB is an embedded lightweight non-relational database

	\subsection{How does it store messages?}
	Messages are stored in file-based data logs. When all of the messages in a data log have been successfully consumed, the data log is marked as deletable. At a predetermined clean-up interval, logs marked as deletable are removed from the system.


	\subsection{What are the files in KahaDB directory?}
		\begin{description}
			\item[db.data] \hfill \\
				The metadata store, mainly B-tree index giving message locations in the data logs. The file is periodically updated from the metadata cache (which is in memory).
			\item[db-n.log] \hfill \\
				These are the journal log files. This is where activeMQ messages will be stored.
			\item[db.free] \hfill \\
				Keeps track of free pages in db.data
			\item[db.redo] \hfill \\
				This is a redo log used to prevent partial page writes from making the file inconsistent.
		\end{description}


	\subsection{Recovering a corrupted metadata store}
	If the metadata store somehow becomes irretrievably corrupted, you can force recovery as follows (assuming the journal's data logs are clean):

	\begin{itemize}
    	\item While the broker is shut down, delete the metadata store, db.data.
    	\item Start the broker.
    	\item The broker now recovers by re-reading the entire journal and replaying all of the events in the journal in order to recreate the missing metadata.
    \end{itemize}
	While this is an effective means of recovering, you should bear in mind that it could take a considerable length of time if the journal is large. Also if the journal logs are dirty, you might not be able to recover the data store. In that case just delete kahadb folder completely and restart the broker.